Improved Bounds for Online Balanced Repartitioning

### 2020-03-28 paper/paper.tex
Reduction not a LB

  We say that the node configuration is \emph{well-aligned} if any of the following conditions hold:
  \begin{enumerate}
    \item One cluster contains $B$ and one node from $A$ and the other cluster contains $C$ and the other node from $A$.
    \item One cluster contains $B$ and one node from $C$ and the other cluster contains $A$ and $k-2$ nodes from set $C$.
    \item (symmetric to the previous condition) One cluster contains $C$ and one node from $B$ and the other cluster contains $A$ and $k-2$ nodes from set $B$.
  \end{enumerate}
  We show a bijection between cache contents and well-aligned configurations.
  We say that a caching node $p_i \in S$, where $S \in \{ A, B, C\}$ belongs to the cache, if the entire set $S$ is collocated in a cluster.
  Otherwise, if $S$ is split

  one cluster
contains the node $s$ and $k-1$ caching nodes, and the other cluster contains
one caching node and all auxiliary nodes. There is a natural bijection between
possible cache contents and well-aligned configurations: the cache consists of
the $k-1$ caching nodes that are in the same cluster as node $s$. (Without loss
of generality, we may assume that the cache of any caching algorithm is always
full, i.e., consists of $k-1$ pages.) If the configuration $c$ of a~BRP
algorithm is well-aligned, $\textsc{cache}(c)$ denotes the corresponding cache
contents.
The initial configuration for the BRP problem is the well-aligned
configuration corresponding to the initial cache (pages
$p_1,p_2,\ldots,p_{k-1}$ in the cache).

We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.
\maciek{define that A,B,C is collocated/split}

Intuitively, if a node is split from other nodes of any of sets $A,B,C$, then it is outside of the cache.
Note that in every configuration, at least one of these sets is split.

>>>>

  We say that the node configuration is \emph{well-aligned} if any of the following conditions hold:
  \begin{enumerate}
    \item One cluster contains $B$ and one node from $A$ and the other cluster contains $C$ and the other node from $A$.
    \item One cluster contains $B$ and one node from $C$ and the other cluster contains $A$ and $k-2$ nodes from set $C$.
    \item (symmetric to the previous condition) One cluster contains $C$ and one node from $B$ and the other cluster contains $A$ and $k-2$ nodes from set $B$.
  \end{enumerate}
  We show a bijection between cache contents and well-aligned configurations.
  We say that a caching node $p_i \in S$, where $S \in \{ A, B, C\}$ belongs to the cache if the entire set $S$ is collocated in a cluster.
  Otherwise, if $p_i$ is located on a different cluster than the other nodes from $S$, we say that it is outside of the cache.
  (Without loss of generality, we may assume that the cache of any caching algorithm is always full, i.e., consists of $k-1$ pages.)
  If the configuration $c$ of a~BRP algorithm is well-aligned, $\textsc{cache}(c)$ denotes the corresponding cache contents.
  The initial configuration for the BRP problem is the well-aligned configuration corresponding to the initial cache (pages $p_1,p_2,\ldots,p_{2k-2}$ in the cache), with sets $A$ and $B$ non-split and the node $p_{2k-1}$ from the set $C$ split.
